---
title: ""
output:
  pdf_document: default
  html_document: default
date: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(tools)
library(psych)
library(tictoc)
library(gridExtra)
library(knitr)
library(cowplot)
```

```{r read_data, cache=TRUE, echo=FALSE, message=FALSE}
rm(list = ls())
walk(
  dir("Data/", full.names = TRUE),
  function(file) {
    assign(file_path_sans_ext(basename(file)), read_tsv(file), .GlobalEnv)
  }
)
tbls <- as.list.environment(.GlobalEnv, sorted = TRUE)

map_stain_num = function(y){
  sapply(y, function(x) switch(x, 3, 1, 2))
}

for(i in seq_along(tbls)){
  tbls[[i]] = tbls[[i]] %>%
    mutate(stain_num = as.character(map_stain_num(floor((i-1/2)/8) + 1)))
}

super_tbl = bind_rows(tbls)
```

# Analysis of Variance

We fit linear models of the form 
\begin{align*}
  \text{dependent\_var} \sim \text{Ligand1} + \text{ECM1} + \text{stain\_num} \tag{1}
\end{align*}
and of the more complicated form
\begin{align*}
  \text{dependent\_var} \sim \text{Ligand1}*\text{ECM1} + \text{stain\_num}. \tag{2}
\end{align*}
For dependent variables which were measured in only one staining set, stain\_num was dropped from the formula. 

The intercept estimates the average value of the dependent variable measured for cells in staining set 1 treated with COL1 and FBS. Note that this treatment uses the control ECMp and control ligand, which makes it a natural baseline for comparison. 

```{r}
lm_analysis = function(var_name, super_tbl, fit_big_lm = FALSE, 
                       print_aov_summary = TRUE){
  lm_super_tbl = super_tbl %>%
  mutate(ECM1 = as.factor(ECM1) %>% 
           relevel(ref = "COL1_go0005584")) %>%
  mutate(Ligand1 = as.factor(Ligand1) %>% 
           relevel(ref = "FBS_pubchemsid56314508")) %>%
    filter(!is.na(.[[var_name]]))

  # ~13.5 minutes
  if(fit_big_lm){
    if(length(unique(lm_super_tbl$stain_num)) == 1){
      area_treatment_lm = aov(
        lm_super_tbl[[var_name]] ~ ECM1*Ligand1,
        data = lm_super_tbl
      )
    } else {
      area_treatment_lm = aov(
        lm_super_tbl[[var_name]] ~ ECM1*Ligand1+stain_num,
        data = lm_super_tbl
      )
    }
    if(print_aov_summary){
      cat(var_name, " interactions model summary: \n")
      print(summary(area_treatment_lm))
      cat("AIC: ", AIC(area_treatment_lm), 
          "; Adjusted R^2: ", summary.lm(area_treatment_lm)$adj.r.squared,
          "\n\n")
    }
  }
  
  if(length(unique(lm_super_tbl$stain_num)) == 1){
    simple_area_treatment_lm = aov(
      lm_super_tbl[[var_name]] ~ ECM1+Ligand1,
      data = lm_super_tbl
    )
  } else {
    simple_area_treatment_lm = aov(
      lm_super_tbl[[var_name]] ~ ECM1+Ligand1+stain_num,
      data = lm_super_tbl
    )
  }
  if(print_aov_summary){
    cat(var_name, " model summary: \n")
    print(summary(simple_area_treatment_lm))
    cat("AIC: ", AIC(simple_area_treatment_lm), 
        "; Adjusted R^2: ", summary.lm(simple_area_treatment_lm)$adj.r.squared,
        "\n\n")  
  }
  
  simple_coefficients_tbl = tibble(
    coefficient = names(simple_area_treatment_lm$coefficients),
    Value = simple_area_treatment_lm$coefficients
  ) %>%
    extract(col = coefficient, 
             into = c("Type", "Treatment"),
             regex = "(Ligand1|ECM1|stain_num|\\(Intercept\\))(.*)") %>%
    mutate(Positive = Value > 0)
  
  simple_coefficients_tbl %>%
    filter(Type == "(Intercept)" | Type == "stain_num") %>%
    select(!Positive) %>%
    kable() %>%
    print()
  
  gg1 = ggplot(simple_coefficients_tbl %>% 
        filter(Type == "ECM1") %>%
        mutate(Treatment = fct_reorder(factor(Treatment), Value)),
    aes(x = Value, y = Treatment, fill = Positive)) +
    geom_col() + 
    theme(legend.position = "none", axis.text.y = element_text(size=5),
          axis.text.x = element_text(size=6),
          plot.title = element_text(size = 10),
          axis.title = element_text(size = 6)) + 
    ylab("ECMP") + 
    xlab("Estimated coefficient")
    
  gg2 = ggplot(simple_coefficients_tbl %>% 
        filter(Type == "Ligand1") %>%
        mutate(Treatment = fct_reorder(factor(Treatment), Value)),
    aes(x = Value, y = Treatment, fill = Positive)) +
    geom_col() + 
    theme(legend.position = "none", axis.text.y = element_text(size=5),
          axis.text.x = element_text(size=6),
          plot.title = element_text(size = 10), 
          axis.title = element_text(size = 7)) + 
    ylab("Ligand") + 
    xlab("Estimated coefficient")
  gg_grid = plot_grid(gg1, gg2)
  gg_title = ggdraw() + 
    draw_label(paste0("Estimated effect of treatment on ", var_name),
               size = 9)
  print(plot_grid(gg_title, gg_grid, ncol=1, rel_heights=c(0.1, 1)))
}
# simple_coefficients_tbl %>%
#     filter(Type == "(Intercept)" | Type == "stain_num") %>%
#     select(!Positive) %>%
#     kable(format = "rst") %>%
#     print()
```

## Nuclei_CP_AreaShape_Area

We'd like to determine whether the ECMp-ligand interactions are worth keeping in the model. The unimportance of such interactions may suggest that further analysis can ignore interactions. 

Based on the following output, model $(1)$ has superior AIC. However, the F-test suggests keeping interaction effects. 

```{r}
lm_analysis("Nuclei_CP_AreaShape_Area", super_tbl, fit_big_lm = FALSE)
```

## Spot_PA_SpotCellCount 

Once again, the simpler linear model has superior AIC while the F-test suggests keeping interaction effects. 

For simplicity, we suggest leaving out interaction effects. 

```{r}
lm_analysis("Spot_PA_SpotCellCount", super_tbl, fit_big_lm = FALSE)
```








