---
title: ""
output:
  pdf_document: default
  html_document: default
date: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(tools)
library(psych)
library(tictoc)
library(gridExtra)
library(knitr)
```

```{r read_data, cache=TRUE, echo=FALSE, message=FALSE}
rm(list = ls())
walk(
  dir("Data/", full.names = TRUE),
  function(file) {
    assign(file_path_sans_ext(basename(file)), read_tsv(file), .GlobalEnv)
  }
)
tbls <- as.list.environment(.GlobalEnv, sorted = TRUE)

map_stain_num = function(y){
  sapply(y, function(x) switch(x, 3, 1, 2))
}

for(i in seq_along(tbls)){
  tbls[[i]] = tbls[[i]] %>%
    mutate(stain_num = as.character(map_stain_num(floor((i-1/2)/8) + 1)))
}

super_tbl = bind_rows(tbls)
```

```{r Big Spearman correlation tibble, eval = FALSE}
tic()
cor_tbl_list = vector(mode = "list", length = length(tbls))
for(i in seq_along(cor_tbl_list)){
  tbls2 = tbls[[i]] %>%
  unite(ECM1, Ligand1, col = "treatment", sep = ":")
  treatments = tbls2[["treatment"]]
  
  tbls_reduced = tbls[[i]] %>%
    select(!(WellIndex:PinDiameter)) %>%
    select(where(is.numeric)) %>%
    select(where(function(x) length(unique(x)) > 8)) %>%
    mutate(treatment = treatments) %>%
    select(treatment, everything()) %>%
    select(!PrintSpot & !ImageID & !ClarionID) %>%
    select(Nuclei_CP_AreaShape_Area | !contains("_AreaShape_")) %>%
    select(!contains("_90_") & !ends_with("_90")) %>%
    select(!contains("_SE_") & !ends_with("_SE")) %>%
    select(!contains("DNA2")) %>%
    select(!contains("_IntegratedIntensity"))
    
  cor_list = vector(mode = "list", length = length(unique(treatments)))
  names(cor_list) = unique(treatments)
  for(j in seq_along(cor_list)){
    treat_tbl = tbls_reduced %>% 
      filter(treatment == unique(treatments)[[j]]) %>%
      select(!treatment) %>%
      select(where(function(x) length(unique(x)) > 1))
    if(length(treat_tbl) != 0){
      cor_test_out = corr.test(treat_tbl, method = "spearman", ci = FALSE,
                               normal = TRUE)
      p_mat_simple = cor_test_out[["p"]]
      p_mat_simple[upper.tri(p_mat_simple)] = 2 # Filters out repeats later
      p_tbl = p_mat_simple %>%
        as.data.frame() %>%
        rownames_to_column(var = "row_var") %>%
        pivot_longer(names_to = "col_var", cols = !matches("row_var")) %>%
        rename(p_val = value)
      cor_list[[j]] = cor_test_out[["r"]] %>%
        as.data.frame() %>%
        rownames_to_column(var = "row_var") %>%
        pivot_longer(names_to = "col_var", cols = !matches("row_var")) %>%
        rename(spear_cor = value) %>%
        left_join(p_tbl, by = c("row_var", "col_var")) %>%
        filter(p_val <= 1, row_var != col_var) %>%
        mutate(treatment = names(cor_list)[[j]], table_num = i) %>%
        select(table_num, treatment, everything()) %>%
        separate(treatment, into = c("ECM1", "Ligand1"), sep = ":", 
                 remove = FALSE) %>%
        mutate(n = cor_test_out[["n"]])
    }
  }
  cor_tbl_list[[i]] = bind_rows(cor_list)
}
big_cor_tbl = bind_rows(cor_tbl_list) %>%
  mutate(stain_num = floor((table_num-1/2)/8) + 1) %>%
  select(stain_num, everything()) %>%
  arrange(p_val) %>%
  filter(n >= 10) %>%
  mutate(row_num = 1:nrow(.)) %>%
  mutate(pass_holm = p_val <= 0.01/(length(row_num) - row_num + 1)) %>%
  select(!row_num) %>%
  unite(col = "relation", row_var, col_var, sep = ":", remove = FALSE) %>%
  mutate(treat = paste0(abbreviate(ECM1),":",abbreviate(Ligand1))) %>%  
  mutate(rel = paste0(abbreviate(row_var),":",abbreviate(col_var))) %>%
  mutate(stain_num = map_stain_num(stain_num))
  
small_big_cor_tbl = big_cor_tbl %>%
  filter(pass_holm == TRUE) %>%
  select(!pass_holm)
# I don't think the p-values equalling 0 are correct but this shouldn't matter
# p-value obtained from t-test
# Could get better p-values using better test but could take a long time
# write_tsv(small_big_cor_tbl, "small_big_cor_tbl.tsv")  
toc()
# 4 minutes to run
```

```{r Load tibbles to save time}
load("big_cor_tbl.rda")
load("small_big_cor_tbl.rda")
```


```{r Frequency of treatments in significant set}
# Doesn't seem interesting
small_big_cor_tbl %>% 
  filter(spear_cor == 1) %>% 
  unite(col = "treat_stain", stain_num, treatment, sep = ":") %>%
  .[["treat_stain"]] %>% 
  table() %>% 
  sort(decreasing = TRUE) -> pos_sig_treat_count
table(pos_sig_treat_count)
pos_sig_treat_count[1:20]
  
small_big_cor_tbl %>% 
  filter(spear_cor == -1) %>% 
  unite(col = "treat_stain", stain_num, treatment, sep = ":") %>%
  .[["treat_stain"]] %>% 
  table() %>% 
  sort(decreasing = TRUE) -> neg_sig_treat_count
table(neg_sig_treat_count)
neg_sig_treat_count[1:20]
```


```{r}
big_cor_tbl %>% 
  group_by(relation, stain_num) %>%
  summarise(cor_vari = var(spear_cor), count = length(spear_cor)) %>%
  arrange(desc(cor_vari)) -> cor_vari_tbl
summary(cor_vari_tbl$cor_vari, na.rm = TRUE)

stuff = vector(mode = "list", length = 6)
for(i in 1:3){
  cor_vari_tbl %>%
    filter(stain_num == i) %>%
    head() -> stuff[[1+2*(i-1)]]
  
  cor_vari_tbl %>%
    filter(stain_num == i) %>%
    tail() -> stuff[[2*i]]
}
(cor_var_summary_tbl = bind_rows(stuff))
```


```{r Big Spearman correlation tibble by LIGAND}
#tic()
cor_tbl_list = vector(mode = "list", length = length(tbls))
for(i in seq_along(cor_tbl_list)){
  tbls_reduced = tbls[[i]] %>%
    select(!(WellIndex:PinDiameter)) %>%
    select(Ligand1, where(is.numeric)) %>%
    select(Ligand1, where(function(x) length(unique(x)) > 8)) %>%
    select(!PrintSpot & !ImageID & !ClarionID) %>%
    select(Nuclei_CP_AreaShape_Area | !contains("_AreaShape_")) %>%
    select(!contains("_90_") & !ends_with("_90")) %>%
    select(!contains("_SE_") & !ends_with("_SE")) %>%
    select(!contains("DNA2")) %>%
    select(!contains("_IntegratedIntensity")) %>%
    select(Ligand1, everything())
    
  cor_list = vector(mode = "list", length = length(unique(tbls_reduced$Ligand1)))
  names(cor_list) = unique(tbls_reduced$Ligand1)
  for(j in seq_along(cor_list)){
    treat_tbl = tbls_reduced %>% 
      filter(Ligand1 == unique(tbls_reduced$Ligand1)[[j]]) %>%
      select(!Ligand1) %>%
      select(where(function(x) length(unique(x)) > 1))
    if(length(treat_tbl) != 0){
      cor_test_out = corr.test(treat_tbl, method = "spearman", ci = FALSE,
                               normal = TRUE)
      p_mat_simple = cor_test_out[["p"]]
      p_mat_simple[upper.tri(p_mat_simple)] = 2 # Filters out repeats later
      p_tbl = p_mat_simple %>%
        as.data.frame() %>%
        rownames_to_column(var = "row_var") %>%
        pivot_longer(names_to = "col_var", cols = !matches("row_var")) %>%
        rename(p_val = value)
      cor_list[[j]] = cor_test_out[["r"]] %>%
        as.data.frame() %>%
        rownames_to_column(var = "row_var") %>%
        pivot_longer(names_to = "col_var", cols = !matches("row_var")) %>%
        rename(spear_cor = value) %>%
        left_join(p_tbl, by = c("row_var", "col_var")) %>%
        filter(p_val <= 1, row_var != col_var) %>%
        mutate(Ligand1 = names(cor_list)[[j]], table_num = i) %>%
        select(table_num, Ligand1, everything()) %>%
        mutate(n = cor_test_out[["n"]])
    }
  }
  cor_tbl_list[[i]] = bind_rows(cor_list)
}
ligand_big_cor_tbl = bind_rows(cor_tbl_list) %>%
  mutate(stain_num = map_stain_num(floor((table_num-1/2)/8) + 1)) %>%
  select(stain_num, everything()) %>%
  arrange(p_val) %>%
  filter(n >= 10) %>%
  mutate(row_num = 1:nrow(.)) %>%
  mutate(pass_holm = p_val <= 0.01/(length(row_num) - row_num + 1)) %>%
  select(!row_num) %>%
  unite(col = "relation", row_var, col_var, sep = ":", remove = FALSE) %>%
  mutate(rel = paste0(abbreviate(row_var),":",abbreviate(col_var)))
  
ligand_small_big_cor_tbl = ligand_big_cor_tbl %>%
  filter(pass_holm == TRUE) %>%
  select(!pass_holm)
# I don't think the p-values equalling 0 are correct but this shouldn't matter
# p-value obtained from t-test
# Could get better p-values using better test but could take a long time
# write_tsv(small_big_cor_tbl, "small_big_cor_tbl.tsv")  
#toc()
# 9 seconds to run
```

```{r Variance of stain-ligand-grouped correlations}
# Don't think that this is helpful
ligand_big_cor_tbl %>% 
  group_by(relation, stain_num) %>%
  summarise(cor_vari = var(spear_cor), count = length(spear_cor)) %>%
  arrange(desc(cor_vari)) -> cor_vari_tbl
```


# Linear model stuff

We fit linear models of the form

\begin{align*}
  \text{dependent\_var} \sim \text{Ligand1} + \text{ECM1} + \text{stain\_num}
\end{align*}
and, in some cases
\begin{align*}
  \text{dependent\_var} \sim \text{Ligand1}*\text{ECM1} + \text{stain\_num}
\end{align*}

The intercept is stain set 1, COL1 for ECM1, and FBS for Ligand1.

For Nuclei_CP_AreaShape_Area: The Simpler linear model (no interaction effects) has superior AIC. However, the F-test suggests keeping interaction effects. 

For Spot_PA_SpotCellCount: Same results as Nuclei_CP_AreaShape_Area

For simplicity, we suggest leaving out interaction effects. 

```{r}
lm_analysis = function(var_name, super_tbl, fit_big_lm = FALSE, 
                       print_aov_summary = TRUE){
  lm_super_tbl = super_tbl %>%
  mutate(ECM1 = as.factor(ECM1) %>% 
           relevel(ref = "COL1_go0005584")) %>%
  mutate(Ligand1 = as.factor(Ligand1) %>% 
           relevel(ref = "FBS_pubchemsid56314508")) %>%
    filter(!is.na(.[[var_name]]))

  # ~13.5 minutes
  if(fit_big_lm){
    if(length(unique(lm_super_tbl$stain_num)) == 1){
      area_treatment_lm = aov(
        lm_super_tbl[[var_name]] ~ ECM1*Ligand1,
        data = lm_super_tbl
      )
    } else {
      area_treatment_lm = aov(
        lm_super_tbl[[var_name]] ~ ECM1*Ligand1+stain_num,
        data = lm_super_tbl
      )
    }
    if(print_aov_summary){
      print(summary(area_treatment_lm))
      cat("AIC: ", AIC(area_treatment_lm), "\n")
    }
  }
  
  if(length(unique(lm_super_tbl$stain_num)) == 1){
    simple_area_treatment_lm = aov(
      lm_super_tbl[[var_name]] ~ ECM1+Ligand1,
      data = lm_super_tbl
    )
  } else {
    simple_area_treatment_lm = aov(
      lm_super_tbl[[var_name]] ~ ECM1+Ligand1+stain_num,
      data = lm_super_tbl
    )
  }
  if(print_aov_summary){
    print(summary(simple_area_treatment_lm))
    cat("AIC: ", AIC(simple_area_treatment_lm), "\n")  
  }
  
  simple_coefficients_tbl = tibble(
    coefficient = names(simple_area_treatment_lm$coefficients),
    Value = simple_area_treatment_lm$coefficients
  ) %>%
    extract(col = coefficient, 
             into = c("Type", "Treatment"),
             regex = "(Ligand1|ECM1|stain_num|\\(Intercept\\))(.*)") %>%
    mutate(Positive = Value > 0)
  
  simple_coefficients_tbl %>%
    filter(Type == "(Intercept)" | Type == "stain_num") %>%
    select(!Positive) %>%
    kable() %>%
    print()
  
  print(ggplot(simple_coefficients_tbl %>% 
        filter(Type == "ECM1") %>%
        mutate(Treatment = fct_reorder(factor(Treatment), Value)),
    aes(x = Value, y = Treatment, fill = Positive)) +
    geom_col() + 
    theme(legend.position = "none", axis.text.y = element_text(size=5)) +
    labs(title = paste0("Estimated effect of ECMP on ", var_name)) + 
    ylab("ECMP") + 
    xlab("Estimated coefficient"))
    
  print(ggplot(simple_coefficients_tbl %>% 
        filter(Type == "Ligand1") %>%
        mutate(Treatment = fct_reorder(factor(Treatment), Value)),
    aes(x = Value, y = Treatment, fill = Positive)) +
    geom_col() + 
    theme(legend.position = "none", axis.text.y = element_text(size=5)) +
    labs(title = paste0("Estimated effect of ligand on ", var_name)) + 
    ylab("Ligand") + 
    xlab("Estimated coefficient"))
}

lm_analysis("Nuclei_CP_AreaShape_Area", super_tbl, fit_big_lm = FALSE)
lm_analysis("Spot_PA_SpotCellCount", super_tbl, fit_big_lm = FALSE)

# simple_coefficients_tbl %>%
#     filter(Type == "(Intercept)" | Type == "stain_num") %>%
#     select(!Positive) %>%
#     kable(format = "rst") %>%
#     print()
```

```{r}
vars_of_note = c(
  "Cells_CP_Intensity_MedianIntensity_CellMask", 
  "Cells_CP_Intensity_MedianIntensity_KRT19",
  "Cells_CP_Intensity_MedianIntensity_KRT5"
)
for(independent_var in vars_of_note){
  lm_analysis(independent_var, super_tbl, fit_big_lm = FALSE, 
              print_aov_summary = FALSE)
}
```






