---
title: "aaron"
output: html_document
date: "2022-09-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tools)
library(psych)
library(tictoc)
library(gridExtra)
```

```{r read_data, cache=TRUE, echo=FALSE, message=FALSE}
rm(list = ls())
walk(
  dir("Data/", full.names = TRUE),
  function(file) {
    assign(file_path_sans_ext(basename(file)), read_tsv(file), .GlobalEnv)
  }
)
tbls <- as.list.environment(.GlobalEnv, sorted = TRUE)

map_stain_num = function(y){
  sapply(y, function(x) switch(x, 3, 1, 2))
}

for(i in seq_along(tbls)){
  tbls[[i]] = tbls[[i]] %>%
    mutate(stain_num = as.character(map_stain_num(floor((i-1/2)/8) + 1)))
}

super_tbl = bind_rows(tbls)
```

Position on the plate seems to affect cell count as evidenced by splotches of low or NA (0?) cell count. Might want to account for this somehow.

```{r, fig.width=12, fig.height=10}
# Spot_PA_SpotCellCount
for(i in seq_along(tbls)){
  print(tbls[[i]] %>%
    ggplot(aes(ArrayColumn, ArrayRow, fill = Spot_PA_SpotCellCount)) +
    facet_wrap(vars(WellIndex, Ligand1)) +
    geom_tile() +
    labs(fill = "Cell Count", title = i) +
    theme_bw()
  )
}
```

```{r, fig.width=12, fig.height=10}
# Spot_PA_SpotCellCount
for(i in 1:8){
  print(tbls[[i]] %>%
    ggplot(aes(ArrayColumn, ArrayRow, fill = Cells_CP_AreaShape_Area)) +
    facet_wrap(vars(WellIndex, Ligand1)) +
    geom_tile() +
    labs(fill = "Cells_CP_AreaShape_Area", title = i) +
    theme_bw()
  )
}
```

Cell count summary stats.

```{r}
cell_ct_summary = sapply(tbls, function(x) 
    summary(x$Spot_PA_SpotCellCount)
  ) %>%
  t() %>%
  as.data.frame() %>%
  rownames_to_column(var = "plate")
cell_ct_summary
```

Median cell count highest for staining set 3. 

```{r}
lapply(seq_along(tbls), function(x)
  data.frame(plate = x, ct = tbls[[x]]$Spot_PA_SpotCellCount)
) %>%
  bind_rows() -> ct_df

ggplot(ct_df, mapping = aes(x = as.factor(plate), y = ct)) + 
  geom_boxplot() + 
  xlab("Plate number") + 
  ylab("Cell count")

ggplot(ct_df, mapping = aes(x = as.factor(plate), y = ct)) + 
  geom_violin() + 
  xlab("Plate number") + 
  ylab("Cell count")
```

Average cell counts grouped by stain/ecmp/ligand.

```{r}
lapply(seq_along(tbls), function(x)
  data.frame(stain = ceiling(x/8),
             ecmp = tbls[[x]]$ECMp,
             ligand = tbls[[x]]$Ligand1,
             ct = tbls[[x]]$Spot_PA_SpotCellCount)
)  %>%
  bind_rows() %>%
  group_by(stain, ecmp, ligand) %>%
  summarise(mean = mean(ct), median = median(ct)) %>%
  arrange(mean) -> ct_sel_summary_df
head(ct_sel_summary_df)
tail(ct_sel_summary_df)
```

Average cell counts grouped by stain/ligand.

```{r}
lapply(seq_along(tbls), function(x)
  data.frame(stain = ceiling(x/8),
             ecmp = tbls[[x]]$ECMp,
             ligand = tbls[[x]]$Ligand1,
             ct = tbls[[x]]$Spot_PA_SpotCellCount)
)  %>%
  bind_rows() %>%
  group_by(stain, ligand) %>%
  summarise(mean = mean(ct), median = median(ct)) %>%
  arrange(mean) -> ct_sl_summary_df
ct_sl_summary_df
```

```{r Big Spearman correlation tibble}
tic()
cor_tbl_list = vector(mode = "list", length = length(tbls))
for(i in seq_along(cor_tbl_list)){
  tbls2 = tbls[[i]] %>%
  unite(ECM1, Ligand1, col = "treatment", sep = ":")
  treatments = tbls2[["treatment"]]
  
  tbls_reduced = tbls[[i]] %>%
    select(!(WellIndex:PinDiameter)) %>%
    select(where(is.numeric)) %>%
    select(where(function(x) length(unique(x)) > 8)) %>%
    mutate(treatment = treatments) %>%
    select(treatment, everything()) %>%
    select(!PrintSpot & !ImageID & !ClarionID) %>%
    select(Nuclei_CP_AreaShape_Area | !contains("_AreaShape_")) %>%
    select(!contains("_90_") & !ends_with("_90")) %>%
    select(!contains("_SE_") & !ends_with("_SE")) %>%
    select(!contains("DNA2")) %>%
    select(!contains("_IntegratedIntensity"))
    
  cor_list = vector(mode = "list", length = length(unique(treatments)))
  names(cor_list) = unique(treatments)
  for(j in seq_along(cor_list)){
    treat_tbl = tbls_reduced %>% 
      filter(treatment == unique(treatments)[[j]]) %>%
      select(!treatment) %>%
      select(where(function(x) length(unique(x)) > 1))
    if(length(treat_tbl) != 0){
      cor_test_out = corr.test(treat_tbl, method = "spearman", ci = FALSE,
                               normal = TRUE)
      p_mat_simple = cor_test_out[["p"]]
      p_mat_simple[upper.tri(p_mat_simple)] = 2 # Filters out repeats later
      p_tbl = p_mat_simple %>%
        as.data.frame() %>%
        rownames_to_column(var = "row_var") %>%
        pivot_longer(names_to = "col_var", cols = !matches("row_var")) %>%
        rename(p_val = value)
      cor_list[[j]] = cor_test_out[["r"]] %>%
        as.data.frame() %>%
        rownames_to_column(var = "row_var") %>%
        pivot_longer(names_to = "col_var", cols = !matches("row_var")) %>%
        rename(spear_cor = value) %>%
        left_join(p_tbl, by = c("row_var", "col_var")) %>%
        filter(p_val <= 1, row_var != col_var) %>%
        mutate(treatment = names(cor_list)[[j]], table_num = i) %>%
        select(table_num, treatment, everything()) %>%
        separate(treatment, into = c("ECM1", "Ligand1"), sep = ":", 
                 remove = FALSE) %>%
        mutate(n = cor_test_out[["n"]])
    }
  }
  cor_tbl_list[[i]] = bind_rows(cor_list)
}
big_cor_tbl = bind_rows(cor_tbl_list) %>%
  mutate(stain_num = floor((table_num-1/2)/8) + 1) %>%
  select(stain_num, everything()) %>%
  arrange(p_val) %>%
  filter(n >= 10) %>%
  mutate(row_num = 1:nrow(.)) %>%
  mutate(pass_holm = p_val <= 0.01/(length(row_num) - row_num + 1)) %>%
  select(!row_num) %>%
  unite(col = "relation", row_var, col_var, sep = ":", remove = FALSE) %>%
  mutate(treat = paste0(abbreviate(ECM1),":",abbreviate(Ligand1))) %>%  
  mutate(rel = paste0(abbreviate(row_var),":",abbreviate(col_var))) %>%
  mutate(stain_num = map_stain_num(stain_num))
  
small_big_cor_tbl = big_cor_tbl %>%
  filter(pass_holm == TRUE) %>%
  select(!pass_holm)
# I don't think the p-values equalling 0 are correct but this shouldn't matter
# p-value obtained from t-test
# Could get better p-values using better test but could take a long time
# write_tsv(small_big_cor_tbl, "small_big_cor_tbl.tsv")  
toc()
# 4 minutes to run
```

```{r Big linear correlation tibble}
tic()
cor_tbl_list = vector(mode = "list", length = length(tbls))
for(i in seq_along(cor_tbl_list)){
  tbls2 = tbls[[i]] %>%
  unite(ECM1, Ligand1, col = "treatment", sep = ":")
  treatments = tbls2[["treatment"]]
  
  tbls_reduced = tbls[[i]] %>%
    select(!(WellIndex:PinDiameter)) %>%
    select(where(is.numeric)) %>%
    select(where(function(x) length(unique(x)) > 8)) %>%
    mutate(treatment = treatments) %>%
    select(treatment, everything()) %>%
    select(!PrintSpot & !ImageID & !ClarionID) %>%
    select(Nuclei_CP_AreaShape_Area | !contains("_AreaShape_")) %>%
    select(!contains("_90_") & !ends_with("_90")) %>%
    select(!contains("_SE_") & !ends_with("_SE")) %>%
    select(!contains("DNA2")) %>%
    select(!contains("_IntegratedIntensity"))
    
  cor_list = vector(mode = "list", length = length(unique(treatments)))
  names(cor_list) = unique(treatments)
  for(j in seq_along(cor_list)){
    treat_tbl = tbls_reduced %>% 
      filter(treatment == unique(treatments)[[j]]) %>%
      select(!treatment) %>%
      select(where(function(x) length(unique(x)) > 1))
    if(length(treat_tbl) != 0){
      cor_test_out = corr.test(treat_tbl, method = "pearson", ci = FALSE,
                               normal = TRUE)
      p_mat_simple = cor_test_out[["p"]]
      p_mat_simple[upper.tri(p_mat_simple)] = 2 # Filters out repeats later
      p_tbl = p_mat_simple %>%
        as.data.frame() %>%
        rownames_to_column(var = "row_var") %>%
        pivot_longer(names_to = "col_var", cols = !matches("row_var")) %>%
        rename(p_val = value)
      cor_list[[j]] = cor_test_out[["r"]] %>%
        as.data.frame() %>%
        rownames_to_column(var = "row_var") %>%
        pivot_longer(names_to = "col_var", cols = !matches("row_var")) %>%
        rename(lin_cor = value) %>%
        left_join(p_tbl, by = c("row_var", "col_var")) %>%
        filter(p_val <= 1, row_var != col_var) %>%
        mutate(treatment = names(cor_list)[[j]], table_num = i) %>%
        select(table_num, treatment, everything()) %>%
        separate(treatment, into = c("ECM1", "Ligand1"), sep = ":", 
                 remove = FALSE) %>%
        mutate(n = cor_test_out[["n"]])
    }
  }
  cor_tbl_list[[i]] = bind_rows(cor_list)
}
big_lin_cor_tbl = bind_rows(cor_tbl_list) %>%
  mutate(stain_num = floor((table_num-1/2)/8) + 1) %>%
  select(stain_num, everything()) %>%
  arrange(p_val) %>%
  filter(n >= 10) %>%
  mutate(row_num = 1:nrow(.)) %>%
  mutate(pass_holm = p_val <= 0.01/(length(row_num) - row_num + 1)) %>%
  select(!row_num) %>%
  unite(col = "relation", row_var, col_var, sep = ":", remove = FALSE) %>%
  mutate(treat = paste0(abbreviate(ECM1),":",abbreviate(Ligand1))) %>%  
  mutate(rel = paste0(abbreviate(row_var),":",abbreviate(col_var))) %>%
  mutate(stain_num = map_stain_num(stain_num))
  
small_big_lin_cor_tbl = big_lin_cor_tbl %>%
  filter(pass_holm == TRUE) %>%
  select(!pass_holm)
# I don't think the p-values equalling 0 are correct but this shouldn't matter
# p-value obtained from t-test
# Could get better p-values using better test but could take a long time
# write_tsv(small_big_lin_cor_tbl, "small_big_lin_cor_tbl.tsv")  
toc()
# 4 minutes to run
```


```{r Frequency of treatments in significant set}
# Doesn't seem interesting
small_big_cor_tbl %>% 
  filter(spear_cor == 1) %>% 
  unite(col = "treat_stain", stain_num, treatment, sep = ":") %>%
  .[["treat_stain"]] %>% 
  table() %>% 
  sort(decreasing = TRUE) -> pos_sig_treat_count
table(pos_sig_treat_count)
pos_sig_treat_count[1:20]
  
small_big_cor_tbl %>% 
  filter(spear_cor == -1) %>% 
  unite(col = "treat_stain", stain_num, treatment, sep = ":") %>%
  .[["treat_stain"]] %>% 
  table() %>% 
  sort(decreasing = TRUE) -> neg_sig_treat_count
table(neg_sig_treat_count)
neg_sig_treat_count[1:20]
```

```{r}
small_big_cor_tbl %>%
  filter(treatment == "TNC|1_P24821|1:FBS_pubchemsid56314508") %>%
  select(row_var, col_var, spear_cor)
```

```{r}
small_big_lin_cor_tbl %>%
  filter(lin_cor < 0.99 & lin_cor > -0.99) %>% 
  View()
```

```{r Focus on somewhat interesting treatments }
tic()
cor_tbl_list = vector(mode = "list", length = length(tbls))
for(i in seq_along(cor_tbl_list)){
  tbls2 = tbls[[i]] %>%
    filter(ECM1 == "OMD_Q99983" | ECM1 == "NID1|1_P14543|1" | 
             ECM1 == "FN1|1_P02751|1" | ECM1 == "ELN|3_P15502|3" |
             ECM1 == "COL5A1_P20908" | ECM1 == "COL4_go0005587" |
             ECM1 == "FBN1_P35555") %>%
    filter(Ligand1 == "BMP2_P12643" | Ligand1 == "GPNMB|1_Q14956|1" |
             Ligand1 == "IGF1|1_P05019|1" | Ligand1 == "NRG1|6_Q02297|6"|
             Ligand1 == "BMP2_P12643" | Ligand1 == "BMP5|1_P22003|1" | 
             Ligand1 == "FGF2|3_P09038|2" | Ligand1 == "CSF2_P04141") %>%
  unite(ECM1, Ligand1, col = "treatment", sep = ":")
  treatments = tbls2[["treatment"]]
  if(length(treatments > 0)){
    tbls_reduced = tbls[[i]] %>%
    filter(ECM1 == "OMD_Q99983" | ECM1 == "NID1|1_P14543|1" | 
             ECM1 == "FN1|1_P02751|1" | ECM1 == "ELN|3_P15502|3" |
             ECM1 == "COL5A1_P20908" | ECM1 == "COL4_go0005587" |
             ECM1 == "FBN1_P35555") %>%
    filter(Ligand1 == "BMP2_P12643" | Ligand1 == "GPNMB|1_Q14956|1" |
             Ligand1 == "IGF1|1_P05019|1" | Ligand1 == "NRG1|6_Q02297|6"|
             Ligand1 == "BMP2_P12643" | Ligand1 == "BMP5|1_P22003|1" | 
             Ligand1 == "FGF2|3_P09038|2" | Ligand1 == "CSF2_P04141") %>%
    select(!(WellIndex:PinDiameter)) %>%
    select(where(is.numeric)) %>%
    select(where(function(x) length(unique(x)) > 8)) %>%
    mutate(treatment = treatments) %>%
    select(treatment, everything()) %>%
    select(!PrintSpot & !ImageID & !ClarionID) %>%
    select(Nuclei_CP_AreaShape_Area | !contains("_AreaShape_")) %>%
    select(!contains("_90_") & !ends_with("_90")) %>%
    select(!contains("_SE_") & !ends_with("_SE")) %>%
      select(!contains("DNA2")) %>%
    select(!contains("_IntegratedIntensity")) 
    
    cor_list = vector(mode = "list", length = length(unique(treatments)))
    names(cor_list) = unique(treatments)
    for(j in seq_along(cor_list)){
      treat_tbl = tbls_reduced %>% 
        filter(treatment == unique(treatments)[[j]]) %>%
        select(!treatment) %>%
        select(where(function(x) length(unique(x)) > 1))
      if(length(treat_tbl) != 0){
        cor_test_out = corr.test(treat_tbl, method = "spearman", ci = FALSE,
                                 normal = TRUE)
        p_mat_simple = cor_test_out[["p"]]
        p_mat_simple[upper.tri(p_mat_simple)] = 2 # Filters out repeats later
        p_tbl = p_mat_simple %>%
          as.data.frame() %>%
          rownames_to_column(var = "row_var") %>%
          pivot_longer(names_to = "col_var", cols = !matches("row_var")) %>%
          rename(p_val = value)
        cor_list[[j]] = cor_test_out[["r"]] %>%
          as.data.frame() %>%
          rownames_to_column(var = "row_var") %>%
          pivot_longer(names_to = "col_var", cols = !matches("row_var")) %>%
          rename(spear_cor = value) %>%
          left_join(p_tbl, by = c("row_var", "col_var")) %>%
          filter(p_val <= 1, row_var != col_var) %>%
          mutate(treatment = names(cor_list)[[j]], table_num = i) %>%
          select(table_num, treatment, everything()) %>%
          separate(treatment, into = c("ECM1", "Ligand1"), sep = ":", 
                   remove = FALSE) %>%
          mutate(n = cor_test_out[["n"]])
      }
    }
    cor_tbl_list[[i]] = bind_rows(cor_list)
  }
}
focus_big_cor_tbl = bind_rows(cor_tbl_list) %>%
  mutate(stain_num = floor((table_num-1/2)/8) + 1) %>%
  select(stain_num, everything()) %>%
  arrange(p_val) %>%
  filter(n >= 10) %>%
  mutate(row_num = 1:nrow(.)) %>%
  mutate(pass_holm = p_val <= 0.01/(length(row_num) - row_num + 1)) %>%
  select(!row_num) %>%
  unite(col = "relation", row_var, col_var, sep = ":", remove = FALSE) %>%
  mutate(treat = paste0(abbreviate(ECM1),":",abbreviate(Ligand1))) %>%  
  mutate(rel = paste0(abbreviate(row_var),":",abbreviate(col_var))) %>%
  mutate(stain_num = map_stain_num(stain_num))
  
focus_small_big_cor_tbl = focus_big_cor_tbl %>%
  filter(pass_holm == TRUE) %>%
  select(!pass_holm)
# I don't think the p-values equalling 0 are correct but this shouldn't matter
# p-value obtained from t-test
# Could get better p-values using better test but could take a long time
# write_tsv(small_big_cor_tbl, "small_big_cor_tbl.tsv")  
toc()
```


```{r Make a bunch of Spearman correlation plots}
cols_per_plot = 40
n_relations = focus_big_cor_tbl$relation %>% 
  unique() %>% 
  length()
n_plots = floor(n_relations/cols_per_plot)
for(i in 1:n_plots){
  focus_big_cor_tbl_filtered = focus_big_cor_tbl %>%
  filter(relation %in% 
           unique(relation)[(1+(cols_per_plot*i)):(cols_per_plot*(i+1))])
  cor_plot = ggplot(focus_big_cor_tbl_filtered, 
        aes(rel, treat, fill = spear_cor)) +
    geom_tile() +
    labs(fill = "Spearman Correlation", title = paste("Plot",i), 
         y = "Treatment", x = "Variable Pair") +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  ggsave(cor_plot, path = "plots", width = 12, height = 7,
         filename = paste0("cor_plot",i,".png"),device = "png")
}

```

```{r}
big_cor_tbl %>% 
  group_by(relation, stain_num) %>%
  summarise(cor_vari = var(spear_cor), count = length(spear_cor)) %>%
  arrange(desc(cor_vari)) -> cor_vari_tbl
summary(cor_vari_tbl$cor_vari, na.rm = TRUE)

stuff = vector(mode = "list", length = 6)
for(i in 1:3){
  cor_vari_tbl %>%
    filter(stain_num == i) %>%
    head() -> stuff[[1+2*(i-1)]]
  
  cor_vari_tbl %>%
    filter(stain_num == i) %>%
    tail() -> stuff[[2*i]]
}
help_me = bind_rows(stuff)

png("help_me.png", height = 30*nrow(help_me), width = 250*ncol(help_me))
grid.table(help_me)
dev.off()

ggplot(cor_vari_tbl) +
  geom_boxplot(mapping = aes(group = stain_num, y = cor_vari))
```

```{r}
stain_set_3 = bind_rows(tbls[1:8])
stain_set_3 %>% 
  transmute(treatment = paste0(ECM1,":",Ligand1)) -> treatments
stain_set_3 %>% 
  select(!(WellIndex:PinDiameter)) %>%
  select(where(is.numeric)) %>%
  select(where(function(x) length(unique(x)) > 8)) %>%
  select(!PrintSpot & !ImageID & !ClarionID) %>%
  mutate(treatment = treatments) %>%
  select(treatment, everything()) %>%
  group_by(treatment) %>%
  summarize(across(everything(), list(mean))) %>%
  ungroup() %>%
  summarize(across(everything(), list(var))) %>%
  t()-> dummy
```


```{r Big Spearman correlation tibble by LIGAND}
tic()
cor_tbl_list = vector(mode = "list", length = length(tbls))
for(i in seq_along(cor_tbl_list)){
  tbls_reduced = tbls[[i]] %>%
    select(!(WellIndex:PinDiameter)) %>%
    select(Ligand1, where(is.numeric)) %>%
    select(Ligand1, where(function(x) length(unique(x)) > 8)) %>%
    select(!PrintSpot & !ImageID & !ClarionID) %>%
    select(Nuclei_CP_AreaShape_Area | !contains("_AreaShape_")) %>%
    select(!contains("_90_") & !ends_with("_90")) %>%
    select(!contains("_SE_") & !ends_with("_SE")) %>%
    select(!contains("DNA2")) %>%
    select(!contains("_IntegratedIntensity")) %>%
    select(Ligand1, everything())
    
  cor_list = vector(mode = "list", length = length(unique(tbls_reduced$Ligand1)))
  names(cor_list) = unique(tbls_reduced$Ligand1)
  for(j in seq_along(cor_list)){
    treat_tbl = tbls_reduced %>% 
      filter(Ligand1 == unique(tbls_reduced$Ligand1)[[j]]) %>%
      select(!Ligand1) %>%
      select(where(function(x) length(unique(x)) > 1))
    if(length(treat_tbl) != 0){
      cor_test_out = corr.test(treat_tbl, method = "spearman", ci = FALSE,
                               normal = TRUE)
      p_mat_simple = cor_test_out[["p"]]
      p_mat_simple[upper.tri(p_mat_simple)] = 2 # Filters out repeats later
      p_tbl = p_mat_simple %>%
        as.data.frame() %>%
        rownames_to_column(var = "row_var") %>%
        pivot_longer(names_to = "col_var", cols = !matches("row_var")) %>%
        rename(p_val = value)
      cor_list[[j]] = cor_test_out[["r"]] %>%
        as.data.frame() %>%
        rownames_to_column(var = "row_var") %>%
        pivot_longer(names_to = "col_var", cols = !matches("row_var")) %>%
        rename(spear_cor = value) %>%
        left_join(p_tbl, by = c("row_var", "col_var")) %>%
        filter(p_val <= 1, row_var != col_var) %>%
        mutate(Ligand1 = names(cor_list)[[j]], table_num = i) %>%
        select(table_num, Ligand1, everything()) %>%
        mutate(n = cor_test_out[["n"]])
    }
  }
  cor_tbl_list[[i]] = bind_rows(cor_list)
}
ligand_big_cor_tbl = bind_rows(cor_tbl_list) %>%
  mutate(stain_num = map_stain_num(floor((table_num-1/2)/8) + 1)) %>%
  select(stain_num, everything()) %>%
  arrange(p_val) %>%
  filter(n >= 10) %>%
  mutate(row_num = 1:nrow(.)) %>%
  mutate(pass_holm = p_val <= 0.01/(length(row_num) - row_num + 1)) %>%
  select(!row_num) %>%
  unite(col = "relation", row_var, col_var, sep = ":", remove = FALSE) %>%
  mutate(rel = paste0(abbreviate(row_var),":",abbreviate(col_var)))
  
ligand_small_big_cor_tbl = ligand_big_cor_tbl %>%
  filter(pass_holm == TRUE) %>%
  select(!pass_holm)
# I don't think the p-values equalling 0 are correct but this shouldn't matter
# p-value obtained from t-test
# Could get better p-values using better test but could take a long time
# write_tsv(small_big_cor_tbl, "small_big_cor_tbl.tsv")  
toc()
# 9 seconds to run
```

```{r Variance of stain-ligand-grouped correlations}
# Don't think that this is helpful
ligand_big_cor_tbl %>% 
  group_by(relation, stain_num) %>%
  summarise(cor_vari = var(spear_cor), count = length(spear_cor)) %>%
  arrange(desc(cor_vari)) -> cor_vari_tbl
```


# Linear model stuff

Intercept is stain set 1, COL1 for ECM1, and FBS for Ligand1.

For Nuclei_CP_AreaShape_Area: Simpler linear model (no interaction effects) has superior AIC. However, F-test suggests keeping interaction effects. 

For Spot_PA_SpotCellCount: Same results as Nuclei_CP_AreaShape_Area

For simplicity, I suggest leaving out interaction effects. 

```{r}
lm_analysis = function(var_name, super_tbl, fit_big_lm = FALSE){
  lm_super_tbl = super_tbl %>%
  mutate(ECM1 = as.factor(ECM1) %>% 
           relevel(ref = "COL1_go0005584")) %>%
  mutate(Ligand1 = as.factor(Ligand1) %>% 
           relevel(ref = "FBS_pubchemsid56314508")) %>%
    filter(!is.na(.[[var_name]]))

  # ~13.5 minutes
  if(fit_big_lm){
    if(length(unique(lm_super_tbl$stain_num)) == 1){
      area_treatment_lm = aov(
        lm_super_tbl[[var_name]] ~ ECM1*Ligand1,
        data = lm_super_tbl
      )
    } else {
      area_treatment_lm = aov(
        lm_super_tbl[[var_name]] ~ ECM1*Ligand1+stain_num,
        data = lm_super_tbl
      )
    }
    
    print(summary(area_treatment_lm))
    cat("AIC: ", AIC(area_treatment_lm), "\n")
  }
  
  if(length(unique(lm_super_tbl$stain_num))){
    simple_area_treatment_lm = aov(
      lm_super_tbl[[var_name]] ~ ECM1+Ligand1,
      data = lm_super_tbl
    )
  } else {
    simple_area_treatment_lm = aov(
      lm_super_tbl[[var_name]] ~ ECM1+Ligand1+stain_num,
      data = lm_super_tbl
    )
  }
  
  print(summary(simple_area_treatment_lm))
  cat("AIC: ", AIC(simple_area_treatment_lm), "\n")
  
  simple_coefficients_tbl = tibble(
    coefficient = names(simple_area_treatment_lm$coefficients),
    Value = simple_area_treatment_lm$coefficients
  ) %>%
    extract(col = coefficient, 
             into = c("Type", "Treatment"),
             regex = "(Ligand1|ECM1|stain_num|\\(Intercept\\))(.*)") %>%
    mutate(Positive = Value > 0)
  
  print(ggplot(simple_coefficients_tbl %>% 
        filter(Type == "ECM1") %>%
        mutate(Treatment = fct_reorder(factor(Treatment), Value)),
    aes(x = Value, y = Treatment, fill = Positive)) +
    geom_col() + 
    theme(legend.position = "none")) +
    labs(title = paste0("Estimated effect of ECMP on ", var_name))
    
  print(ggplot(simple_coefficients_tbl %>% 
        filter(Type == "Ligand1") %>%
        mutate(Treatment = fct_reorder(factor(Treatment), Value)),
    aes(x = Value, y = Treatment, fill = Positive)) +
    geom_col() + 
    theme(legend.position = "none")) +
    labs(title = paste0("Estimated effect of ligand on ", var_name))
  
  simple_coefficients_tbl %>%
    filter(Type == "(Intercept)" | Type == "stain_num") %>%
    select(!Positive) %>%
    print()
}

lm_analysis("Nuclei_CP_AreaShape_Area", super_tbl, fit_big_lm = FALSE)
lm_analysis("Spot_PA_SpotCellCount", super_tbl, fit_big_lm = FALSE)

```








